---
output: github_document
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# timeulaR

Timeular ZEI is a tangible time tracking solution. This package is a wrapper for the Timeular public API.

## Installation

You can install timeulaR from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Steensson/timeulaR")
```

## Obtain access token

With this endpoint you can obtain Access Token required to access secured endpoints.
To do so, you have to provide API Key & API Secret.
They can be generated on the profile website (https://profile.timeular.com/#/login).

```{r example_signIn, eval = FALSE}
apiKey <- "ABCDefgh1234="
apiSecret <- "EFGHijkl5678="
token <- timeulaR::signIn(apiKey, apiSecret)
```

## Fetch user's profile

```{r example_userProfile, eval = FALSE}
token <- "123456789"
timeulaR::userProfile(token, as_df = TRUE)
#    userId          email firstName  lastName
#  1   7030 ses@damvad.com Sebastian Steenssøn
```
