---
output: github_document
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# timeulaR

Timeular ZEI is a tangible time tracking solution. This package is a wrapper for the Timeular public API.

## Installation

You can install timeulaR from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Steensson/timeulaR")
```


## Obtain access token

With this endpoint you can obtain Access Token required to access secured endpoints.
To do so, you have to provide API Key & API Secret.
They can be generated on the profile website (https://profile.timeular.com/#/login).

```{r example_signIn, eval = FALSE}
apiKey <- "ABCDefgh1234="
apiSecret <- "EFGHijkl5678="
token <- timeulaR::signIn(apiKey, apiSecret)
```


## Fetch user's profile

With this function you can fetch your profile data.

```{r example_userProfile, eval = FALSE}
token <- "123456789"
timeulaR::userProfile(token, as_df = TRUE)
#    userId          email firstName  lastName
#  1   7030 ses@damvad.com Sebastian Steenssøn
```


## Fetch API key

With this function you can fetch your API Key.

```{r example_fetchKey, eval = FALSE}
token <- "123456789"
timeulaR::fetchKey(token)
```


## Generate new API Key & API Secret

With this function you can generate new pair of API Key & API Secret.
Every time you generate a new pair, an old one becomes invalid.
Your API Secret won’t be accessible later, so please note it down in some secret place.
If you have lost your API Secret, you can generate a new pair of API Key & API Secret here.

```{r example_generateKeys, eval = FALSE}
token <- "123456789"
timeulaR::generateKeys(token)
```
